Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands

### 2024-02-13 paper/paper.qmd
Updated quarto file
Made some changes to quarto file and added a new figure

>>>>

```{r}
#| label: fig-testscoresela
#| echo: false
#| message: false
#| fig-cap: "Update"
library(tidyverse)
library(janitor)
library(dplyr)
library(knitr)
library(here)
library(readxl)
library(ggplot2)
library(patchwork)

# Filter for Math
filtered_test_data <- cleaned_test_score_data |>
  filter(subject == "ELA")
